Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-04-02 document/ms.tex
re-focus abstract on the method, including uncertainties

\begin{abstract}
Although no true extra-solar Earth analog is known, hundreds of planets have
been found around Sun-like stars that are either Earth-sized but on shorter
periods, or else on year-long orbits but somewhat bigger than Earth.
These populations ought to permit a (possibly highly uncertain) extrapolated
measurement of the probability or rate at which Sun-like stars host true Earth
analogs.
Here we build a set of probabilistic models of the population of known small
planets around G dwarfs.
The models take into account the transit probability and the completeness
(or detection efficiency) as a function of planet radius and orbital period.
Because we forward model the data, we do not ever have to perform any kind of
inverse-detection-efficiency weighting of the data.
Our most sophisticated models do not assume that the joint radius--period
distribution is separable.
They also correctly take into account the significant observational
uncertainties on the planet radii, using the machinery of hierarchical
inference.
We reconsider and confirm with weaker assumptions prior results on the
distribution of exoplanet radii that show a flattening of the distribution
below a few Earth radii.
One output of our models is fully marginalized estimates---marginalizing out
observational uncertainties and all distribution parameters---of the rate
density of true Earth analogs, expressed as a number of planets per star per
natural logarithmic interval of period and radius, evaluated at the properties
of Earth.
The rate density we infer is an extrapolation; it depends strongly on the
permitted flexibility of the distribution model, but it tends to come out
at around ten percent, with large uncertainty.
\end{abstract}

>>>>

\begin{abstract}
Although no true extra-solar Earth analog is known, hundreds of planets have
been found around Sun-like stars that are either Earth-sized but on shorter
periods, or else on year-long orbits but somewhat bigger than Earth.
These populations ought to permit a (possibly highly uncertain) extrapolated
measurement of the probability or rate at which Sun-like stars host true Earth
analogs.
Here we present a general probabilistic framework for making justified
inferences about the occurrence rate of exoplanets taking into account survey
completeness \emph{and observational uncertainties}.
We demonstrate that our method produces lower variance estimates than the
standard inverse-detection-efficiency weighting procedure.
When applied to an existing catalog of small planet candidates around G dwarfs
(Petigura \etal 2013), our method confirms previous measurements of a
flattening radius distribution near Earth's radius.
One output of our models is fully marginalized estimates---marginalizing out
observational uncertainties and all distribution parameters---of the rate
density of true Earth analogs, expressed as a number of planets per star per
natural logarithmic interval of period and radius, evaluated at the properties
of Earth.
The rate density we infer is an extrapolation; it depends strongly on the
permitted flexibility of the distribution model, but it tends to come out
at around ten percent, with large uncertainty.
\end{abstract}
